Sagan Fellowship Previous and Current Research Statement: \\ Giant Planet Formation and Snowlines in Protoplanetary Disks

### 2015-11-04 Postdoc Applications/AnaMariaPisoResume.tex
update

\section{\sc Education}
{\bf Harvard University}, Cambridge, MA \\
\begin{list1}
\vspace{-0.1in}
\item[] Ph.D., Astronomy \& Astrophysics, May 2016 (expected)
\item[] Advisor: Dr. Karin \"Oberg 
\item[] Thesis Topic: ``The Effect of Disk Chemistry and Dynamics in Shaping Volatile Snowlines''   
\end{list1}
{\bf Harvard University}, Cambridge, MA \\
\begin{list1}
\vspace{-0.1in}
\item[] A.M., Astronomy \& Astrophysics, May 2013
\item[] Advisor: Dr. Ruth Murray-Clay
\item[] Research Exam Project: ``On the Minimum Core Mass for Giant Planet Formation''
\end{list1}
{\bf Massachusetts Institute of Technology}, Cambridge, MA\\
%{\em Department of Statistics} 
\vspace*{-.1in}
\begin{list1}
\item[] S.B., Physics,  June 2010 \,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\, Major GPA: 4.6/5.0
\item[] S.B., Mathematics, June 2010\,\,\,\, Major GPA: 4.8/5.0
\end{list1}

@@

\begin{list2}
\item[] {\bf Piso, A.-M. A.}, \"Oberg, K. I., Birnstiel, T., \& Murray-Clay, R. A. \textit{C/O and Snowline Locations in Protoplanetary Disks: The Effect of Radial Drift and Viscous Gas Accretion}. ApJ, under review \\
\end{list2}

@@

>>>>

\section{\sc Education}
{\bf Harvard University}, Cambridge, MA \\
\begin{list1}
\vspace{-0.1in}
\item[] Ph.D., Astronomy \& Astrophysics, May 2016 (expected)
\item[] Advisor: Dr. Karin \"Oberg 
\item[] Thesis Topic: ``Dynamics and Chemistry in Protoplanetary Disks''   
\end{list1}
{\bf Harvard University}, Cambridge, MA \\
\begin{list1}
\vspace{-0.1in}
\item[] A.M., Astronomy \& Astrophysics, May 2013
\item[] Advisor: Dr. Ruth Murray-Clay
\item[] Research Exam Project: ``On the Minimum Core Mass for Giant Planet Formation''
\end{list1}
{\bf Massachusetts Institute of Technology}, Cambridge, MA\\
%{\em Department of Statistics} 
\vspace*{-.1in}
\begin{list1}
\item[] S.B., Physics,  June 2010 \,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\, Major GPA: 4.6/5.0
\item[] S.B., Mathematics, June 2010\,\,\,\, Major GPA: 4.8/5.0
\end{list1}

@@

\begin{list2}
\item[] {\bf Piso, A.-M. A.}, \"Oberg, K. I., Birnstiel, T., \& Murray-Clay, R. A. \textit{C/O and Snowline Locations in Protoplanetary Disks: The Effect of Radial Drift and Viscous Gas Accretion}. ApJ, resubmitted after referee report \\
\end{list2}

@@

\begin{list2}
\item[] {\bf C/O and Snowline Locations in Protoplanetary Disks: The Effect of Radial Drift and Viscous Gas Accretion} \\
Extreme Solar Systems III, Waikoloa, HI, December 2015 \\
Poster \\
\end{list2}
